\documentclass[a4paper,10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue
}

% Section styling
\titleformat{\section}{\large\bfseries\color{black}}{}{0em}{}[\titlerule]

% Custom commands
\newcommand{\name}[1]{\centerline{\Huge \bfseries #1}}
\newcommand{\contact}[1]{\centerline{#1}}
\newcommand{\sectionspace}{\vspace{8pt}}

\begin{document}

\name{MOK Owen}
\contact{\href{mailto:owenmok202@outlook.com}{owenmok202@outlook.com} ~|~ +852-66860710 ~|~ github.com/Mokmokhi ~|~ linkedin.com/in/owen-mok-a150052a3/}
\sectionspace

\section*{Summary}
A self-motivated programmer with sufficient foundation in Mathematics and supportive knowledge in Computer Science. Experienced in Python, C++, and web development. Passionate about building efficient software solutions and exploring new technologies, especially in exploring various algorithms.

\section*{Skills}
\begin{multicols}{2}
\begin{itemize}[leftmargin=*]
  \item \textbf{Languages:} Python, C++, C\#, Pascal
  \item \textbf{Web:} HTML5, CSS3, React, Node.js
  \item \textbf{Frameworks:} Django, Flask, Express
  \item \textbf{Tools:} Git, Linux, VSCode
  \item \textbf{Databases:} MongoDB, AWS DynamoDB, MySQL
  \item \textbf{Machine Learning:} PyTorch, TensorFlow, Scikit-learn
  \item \textbf{Other:} LaTeX, Obsidian, LEAN4
\end{itemize}
\end{multicols}

\section*{Projects}
\textbf{AutoGNN Framework} \hfill \textit{Python, PyTorch, NetworkX} \\
Built a modular GNN pipeline for representation learning and region-of-interest discovery, with interpretable attention modules and offline RL training via Conservative Q-Learning. \\
\textit{Highlights: custom GAT and VGAE modules, ROI agent with actor-critic, dynamic entropy penalty modeling.}\\

\noindent\textbf{Pacman} \hfill \textit{C\#} \\
Developed a Pacman game using C\# with a custom AI agent that simulate NPC's actions. The first successful project with university teammates.

\section*{Work Experience}
\textbf{Tutor, Total Wise Limited} \hfill \textit{Jun 2023 -- Aug 2025} \\
\begin{itemize}[leftmargin=*]
  \item Preparing and distributing learning materials for colleagues using LaTeX.
  \item Deeply explain mathematical logic to highschool students with attractive thoughts.
  \item Sharing teaching understanding with co-workers, improving the working strategies.
\end{itemize}

\section*{Education}
\textbf{M. Sc. in Mathematics} \hfill \textit{Expected Graduation: Aug 2026} \\
The Chinese University of Hong Kong \\
\textit{Relevant Courses:} Mathematical Principles of Artificial Intelligence (A), Topics in Number Theory (A), Computational Mathematics (A-), Linear Analysis (A-)\\

\noindent\textbf{B.Sc. in Mathematics} \hfill \textit{Gaduated: Aug 2023} \\
The Chinese University of Hong Kong \\
\textit{Relevant Courses:} Computer Principles and C++ Programming (A), Software Engineering (A), Fundamental in Machine Learning (B+), Optimization Theory (B+), Game Theory (B+)

\section*{Languages}
Chinese (Native), English (Fluent), Mandarin (Fluent), Japanese (Intermediate)

\end{document}
% End of cv.tex